Cybersecurity Education and Accreditation:\\A Case Study of the UK

### 2019-06-22 FIE2019-final-TPJHD.tex
Further edits round PCIDSS

This can be further illustrated by the demands of particular sectors for secure software. Considering the case of the Payments Industry \cite[6.6]{PCI2018b} which insists on either independent code reviews by security specialists or a Web Application Firewall: essentially saying that the normal development process even after developers are trained in secure coding practices \cite[6.5]{PCI2018b} cannot be trusted to deliver secure code.

\section{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The general public --- this is important, but there are many initiatives in this area (e.g. Cyber Essentials\footnote{Cyber Essentials is a UK Government-backed, industry-supported scheme to help organisations protect themselves against common online threats: \url{https://www.cyberessentials.ncsc.gov.uk}}, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general computer science graduate.
\item The generalist computer science masters graduate.
\item The specialist computer science graduate.
\item The specialist computer science masters graduate.
\end{enumerate}
The focus of this paper is on 2-3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science  students?
\item[RQ2]Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?
\item[RQ3]Can accreditation by professional, statutory and regulatory bodies (PSRBs) enhance the provision of cybersecurity within a body's jurisdiction?
\end{description}

@@

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]BCS, The Chartered Institute for IT (BCS) has had a requirement to include information security in the curriculum since 2010, and has expected coverage of an agreed cybersecurity syllabus since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle). More precisely, accredited degrees have been expected to demonstrate coverage of ``2.1.9 Knowledge and understanding of information security issues in relation to the design, development and the use of information  systems'' \cite[p.~30]{BCS2018a} since 2010 with an enhanced cybersecurity related definition of what this entails since 2015 \cite[p.~17--18]{BCS2018a}.
%BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 July 2019): more precisely \cite[Table 3]{Oudshoornetal2018a} ``The computing topics must include: \dots{} Principles and practices for secure computing \dots. This should mean that  all accredited universities should be compliant by 2025 (because of the six-year cycle).
%\cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}

@@

% Drop2019 was awarded the (unique) best paper at SIGCSE2019 - not sure what to make of this.
Hence \cite{Drop2019} analysed the database textbooks used by  44 of the top 50 Computer Science
departments in the United States. % (using \cite{StangerMartin2015a}'s list, the other six didn't have a book listed). 
There were seven such books, but three books accounted for the 36 of the 44 universities. Five of the seven (30 of the 44) had no mention of SQL injection. On the other two, the more popular one has a seriously flawed discussion\footnote{``However, the paper implies that using parameters is equivalent to using a function to add escape characters
around user input. This is incorrect, as using parameters allows
SQL statements to be pre-compiled, and prevents any user input
from being interpreted as code, while escaping user input is not
recommended as a sole defense since imperfect escape functions
can easily be subverted.'' \cite{Drop2019}}, and the other, while generally excellent, had a presentational problem\footnote{``However, the fact that the first
example should not be used is not discussed until two pages after
the example in the text, and is not mentioned at all in the caption or
on the page where the figure appears. This means a student who is
skimming the text looking for an example to modify for their own
code could simply copy the code that first appears in the example,
without being aware that this is in fact an example of what they
shouldn't do.'' \cite{Drop2019}}.
\par
This oversight is not limited to textbooks: although Wikipedia has an article on SQL Injection, it was not linked from the SQL page itself.\footnote{Fixing this is a suggestion for future work.}
\subsubsection{The case of Java}\label{sec:Java}
A recommendation for future work is a comprehensive survey equivalent to \cite{Drop2019} for  Java textbooks. Indeed, many such books go nowhere near security applications.  But this means that the programmer who has to implement security is left to the documentation of the package/API being used, and to informal resources. \cite{Mengetal2018a} analysed 503 cybersecurity-related postings on the popular Stack overflow (\url{https://stackoverflow.com}) resource.  53\% were about the Spring Security framework (\url{https://projects.spring.io/spring-security/}), dominated by authentication (45\%). The discussion \cite[\S4.3.1]{Mengetal2018a} of cross-site request forgery (CSRF) is especially worrying.  By default, Spring implicitly enables protection against this. But all the accepted answers to CSRF-related failures simply suggested disabling they check. There were no negative comments about this, and indeed a typical response is ``Adding \verb!csrf().disable()!
solved the issue!!! I have no idea why it was enabled by default''. As of writing (16 January 2018) there were no negative comments about this disabling of a vital security feature.
\par
This research was further developed by \cite{Chenetal2019a}  (and popularised in a security community in \cite{Zorz2019a}). Their first finding was
\begin{quote}
644 out of the 1,429 inspected answer posts
(45\%) are insecure, meaning that insecure suggestions
popularly exist on SO. Insecure answers dominate, in
particular, the SSL/TLS category [355 insecure versus 150 secure, i.e. $>70$\%].
\end{quote}

>>>>

This can be further illustrated by the demands of particular sectors for secure software. Considering the case of the Payments Industry \cite[6.6]{PCI2018b} which insists on either independent code reviews by security specialists or a Web Application Firewall: essentially saying that the normal development process, even after developers are trained annually in secure coding practices \cite[6.5]{PCI2018b}, cannot be trusted to deliver secure code.

\section{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The general public --- this is important, but there are many initiatives in this area (e.g. Cyber Essentials\footnote{Cyber Essentials is a UK Government-backed, industry-supported scheme to help organisations protect themselves against common online threats: \url{https://www.cyberessentials.ncsc.gov.uk}.}), which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general computer science graduate.
\item The generalist computer science masters graduate.
\item The specialist computer science graduate.
\item The specialist computer science masters graduate.
\end{enumerate}
The focus of this paper is on 2-3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science  students?
\item[RQ2]Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?
\item[RQ3]Can accreditation by professional, statutory and regulatory bodies (PSRBs) enhance the provision of cybersecurity within a body's jurisdiction?
\end{description}

@@

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]BCS, The Chartered Institute for IT (BCS) has had a requirement to include information security in the curriculum since 2010, and has expected coverage of an agreed cybersecurity syllabus since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle). More precisely, accredited degrees have been expected to demonstrate coverage of ``2.1.9 Knowledge and understanding of information security issues in relation to the design, development and the use of information  systems'' \cite[p.~30]{BCS2018a} since 2010 with an enhanced cybersecurity related definition of what this entails since 2015 \cite[p.~17--18]{BCS2018a}.
%BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 July 2019): more precisely \cite[Table 3]{Oudshoornetal2018a} ``The computing topics must include: \dots{} Principles and practices for secure computing \dots''. This should mean that  all accredited universities should be compliant by 2025 (because of the six-year cycle).
%\cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}

@@

% Drop2019 was awarded the (unique) best paper at SIGCSE2019 - not sure what to make of this.
Hence \cite{Drop2019} analysed the database textbooks used by  44 of the top 50 Computer Science
departments in the United States. % (using \cite{StangerMartin2015a}'s list, the other six didn't have a book listed). 
There were seven such books, but three books accounted for the 36 of the 44 universities. Five of the seven (30 of the 44) had no mention of SQL injection. On the other two, the more popular one has a seriously flawed discussion\footnote{``However, the paper implies that using parameters is equivalent to using a function to add escape characters
around user input. This is incorrect, as using parameters allows
SQL statements to be pre-compiled, and prevents any user input
from being interpreted as code, while escaping user input is not
recommended as a sole defense since imperfect escape functions
can easily be subverted.'' \cite{Drop2019}}, and the other, while generally excellent, had a presentational problem\footnote{``However, the fact that the first
example should not be used is not discussed until two pages after
the example in the text, and is not mentioned at all in the caption or
on the page where the figure appears. This means a student who is
skimming the text looking for an example to modify for their own
code could simply copy the code that first appears in the example,
without being aware that this is in fact an example of what they
shouldn't do.'' \cite{Drop2019}}.
\par
This oversight is not limited to textbooks: although Wikipedia has an article on SQL Injection, it was not linked from the SQL page itself.\footnote{Fixing this is a suggestion for future work.}
\subsubsection{The case of Java}\label{sec:Java}
A recommendation for future work is a comprehensive survey equivalent to \cite{Drop2019} for  Java textbooks. Indeed, many such books go nowhere near security applications.  But this means that the programmer who has to implement security is left to the documentation of the package/API being used, and to informal resources. \cite{Mengetal2018a} analysed 503 cybersecurity-related postings on the popular Stack overflow (\url{https://stackoverflow.com}) resource.  53\% were about the Spring Security framework (\url{https://projects.spring.io/spring-security/}), dominated by authentication (45\%). The discussion \cite[\S4.3.1]{Mengetal2018a} of cross-site request forgery (CSRF) is especially worrying.  By default, Spring implicitly enables protection against this. But all the accepted answers to CSRF-related failures simply suggested disabling the check. There were no negative comments about this, and indeed a typical response is ``Adding \verb!csrf().disable()!
solved the issue!!! I have no idea why it was enabled by default''. As of writing (16 January 2018) there were no negative comments about this disabling of a vital security feature.
\par
This research was further developed by \cite{Chenetal2019a}  (and popularised in a security community in \cite{Zorz2019a}). Their first finding was
\begin{quote}
644 out of the 1,429 inspected answer posts
(45\%) are insecure, meaning that insecure suggestions
popularly exist on SO. Insecure answers dominate, in
particular, the SSL/TLS category [355 insecure versus 150 secure, i.e. $>70$\%].
\end{quote}
